### 2016-07-03 ansi-isolation.tex
Edits.

Snapshot visibility (\C{SnapshotVis}) captures the scenario where a
transaction executes against a static snapshot of the database.  A
transaction $T_i$ is said to be snapshot-visible to a transaction
$T_j$ if either it is visible to $T_j$ (i.e., $T_i$ is included in the
snapshot), or it is invisible (i.e., it is not included); it is
forbidden for only a suffix (more generally, a subset) of $T_j$ to
witness $T_i$. \iso{Repeatable Read} ({\sc rr}) isolation extends {\sc
mav} with the snapshot visibility guarantee.  Observe that snapshot
visibility permits $T_i$ and $T_j$ to execute and commit while being
oblivious of each other. This scenario is captured in
Fig.~\ref{fig:ansi-iso-eg-rr}, where transactions $T_1$ and $T_2$,
which perform conflicting writes, execute against a snapshot of the
database and commit concurrently. While the actual values read and
written by $T_1$ and $T_2$ are unimportant (hence, elided), it is
important to note the \emph{absence} of visiblity arrows from $T_2$ to
$T_1$, although $T_2$ commits before $T_1$'s read-from-$Y$.

>>>>

Snapshot visibility (\C{SnapshotVis}) captures the scenario where a
transaction executes against a static snapshot of the database.  A
transaction $T_i$ is said to be snapshot-visible to a transaction
$T_j$ if either it is visible to $T_j$ (i.e., $T_i$ is included in the
snapshot), or it is invisible (i.e., it is not included); it is
forbidden for only a suffix (more generally, a subset) of $T_j$ to
witness $T_i$. Specification of ANSI SQL \iso{Repeatable Read}
isolation (\C{RR}) extends \C{MAV} with the snapshot visibility
guarantee.  Observe that snapshot visibility permits $T_i$ and $T_j$
to execute and commit while being oblivious of each other. This
scenario is captured in Fig.~\ref{fig:ansi-iso-eg-rr}, where
transactions $T_1$ and $T_2$, which perform conflicting writes,
execute against a snapshot of the database and commit concurrently.
While the actual values read and written by $T_1$ and $T_2$ are
unimportant (hence, elided), it is important to note the
\emph{absence} of visiblity arrows from $T_2$ to $T_1$, although $T_2$
commits before $T_1$'s read-from-$Y$.
